VM-centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-30 snapshot_system/paper_analysis.tex
updated VO/VC VM->FSB mapping figure with N0/1/2.
Rich tightens a bit
as dense as I could make it

\begin{table}[htbp]
\centering
\tabcolsep=0.11cm
\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
%\hline
%$k$ &  the number of top most popular chunks selected for deduplication\\ 
%\hline
%$c$ &  the total amount of data chunks in a cluster of VMs\\ 
%\hline
%$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
%\hline
%$f_i$ &  the frequency for the $i$th most popular fingerprint\\
%\hline
%$\delta$ &  the percentage of duplicates detected in local deduplication\\
%\hline
%$\sigma$ & = percentage of unique data  belonging to  PDS\\
\hline
$r$, $r_c$ & replication degree of non-PDS, and PDS file blocks in VC\\
\hline
$n$, $p$ & no. of virtual and physical machines in the cluster\\
%\hline
%$V$ & the average number of VMs per machine\\
%\hline
%$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$, $N_2$ & the average number  of non-PDS and PDS file blocks in a VM for VC\\
\hline
$N_o$ & the average number  of file blocks  in a VM for VO\\
\hline
A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

\subsection{ Impact on Fault Isolation}

@@

For VC, each VM has an average number $N_1$ of non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS block is associated with one VM
 and  we denote that PDS blocks are
shared by an average of $V_c$ VMs. 
Then, 
\[
n* N_1   \approx \mbox{ No of non-PDS file system blocks} 
\]

For VO, each VM has an average of $N_o$ file system blocks
and let $V_o$ be the average number of VMs shared by each file block.
\[
n *N_o   =  V_o *\mbox{ No of file system blocks} 
\]

@@

For VC, there are two cases: 
\begin{itemize}
\item
When $r \le d<r_c$,  there is no PDS data loss and we need to look at the non-PDS data loss. 
The full snapshot availability of a VM is: 
%\begin{equation}
%\label{eq:VC1}
%(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
\[
A(r)^{N_1}.
\]
%\end{equation}
Since $N_1$ is typically much smaller than $N_o$, 
the VC approach has a higher availability of VM snapshots than VO in this case.
%In the evaluation discussed in Section~\ref{sect:evaldedup}, 
%We have considered a worst case scenario where
%every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
%Even with $N_2$ being much higher than $N_o$ (as discussed below),
%the availability of VC snapshots is much higher than VO.

\item
When $r_c \leq d$, both non-PDS and PDS file system blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
%\begin{equation}
%\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\[
A(r)^{N_1} * A(r_c)^{N_2}.
\]
That is still smaller than that of $V_O$ based on the observation with our data. There are two reasons for this:  
1) $N_1$ is much smaller than $N_o$ and we are observing that $N_1+N_2<N_o$. 
2)  $A(r) < A(r_c)$ because $r < r_c$.  
Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
%that the availability of an individual file system block
different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.
%\end{equation}
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize} 
%In the evaluation discussed in Section~\ref{sect:evaldedup},
%We have considered a worst case scenario that
%every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
%Even with that, the availability of VC snapshots is still much higher than VO and

>>>>

%\begin{table}[htbp]
\begin{table}[t]
\centering
\tabcolsep=0.11cm
\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
%\hline
%$k$ &  the number of top most popular chunks selected for deduplication\\ 
%\hline
%$c$ &  the total amount of data chunks in a cluster of VMs\\ 
%\hline
%$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
%\hline
%$f_i$ &  the frequency for the $i$th most popular fingerprint\\
%\hline
%$\delta$ &  the percentage of duplicates detected in local deduplication\\
%\hline
%$\sigma$ & = percentage of unique data  belonging to  PDS\\
\hline
$r$, $r_c$ & replication degree of non-PDS, and PDS file blocks in VC\\
\hline
$n$, $p$ & no. of virtual and physical machines in the cluster\\
%\hline
%$V$ & the average number of VMs per machine\\
%\hline
%$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$, $N_2$ & the average number  of non-PDS and PDS file blocks in a VM for VC\\
\hline
$N_o$ & the average number  of file blocks  in a VM for VO\\
\hline
A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

\subsection{Fault Isolation}

@@

For VC, each VM has an average number $N_1$ of non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS block is associated with one VM
 and  we denote that PDS blocks are
shared by an average of $V_c$ VMs. 
Then, 
\[
n* N_1   \approx \mbox{ Number of non-PDS file system blocks} 
\]

For VO, each VM has an average of $N_o$ file system blocks
and let $V_o$ be the average number of VMs shared by each file block.
\[
n *N_o   =  V_o *\mbox{ Number of file system blocks} 
\]

@@

For VC, there are two cases: $r \le d<r_c$ and $r_c \leq d$.

\noindent $r \le d<r_c$:  In this case there is no PDS data loss and we need to look at the non-PDS data loss. 
The full snapshot availability of a VM is: 
%\begin{equation}
%\label{eq:VC1}
%(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
\[
A(r)^{N_1}.
\]
%\end{equation}
Since $N_1$ is typically much smaller than $N_o$, 
the VC approach has a higher availability of VM snapshots than VO in this case.
%In the evaluation discussed in Section~\ref{sect:evaldedup}, 
%We have considered a worst case scenario where
%every PDS FSB is shared by all VMs in the VC approach, which leads a large $N_2$ value. 
%Even with $N_2$ being much higher than $N_o$ (as discussed below),
%the availability of VC snapshots is much higher than VO.

\noindent $r_c \leq d$: Both non-PDS and PDS file system blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
%\begin{equation}
%\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\[
A(r)^{N_1} * A(r_c)^{N_2}.
\]
That is still smaller than that of $V_O$ based on the observation with our data. There are two reasons for this:  
1) $N_1$ is much smaller than $N_o$ and we are observing that $N_1+N_2<N_o$. 
2)  $A(r) < A(r_c)$ because $r < r_c$.  
Table~\ref{tab:fsb-availability} lists the $A(r)$ values with
%that the availability of an individual file system block
different replication degrees, to demonstrate the gap between  $A(r)$ and  $A(r_c)$.
%\end{equation}
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
%In the evaluation discussed in Section~\ref{sect:evaldedup},
%We have considered a worst case scenario that
%every PDS FSB is shared by all VMs in the VC approach, which leads to a large $N_2$ value. 
%Even with that, the availability of VC snapshots is still much higher than VO and
